---
title: "R Notebook for all B. abortus tree; rhierBAPS analysis"
date: "June 2nd, 2019"
author: "Marcela Suarez-Esquivel"
output: html_notebook
---

Subset with all B. abortus included in the analysis. Only other terrestrial Brucella species (B. melitensis, B. canis, etc.) were excluded.


#Importing libraries


```{r}
library(rhierbaps)
library(ggtree)
library(phytools)
library(ape)
```

#Loading data

```{r}
abortus.aln <-system.file("BabCR", "all-abortus.aln", package = "rhierbaps")

all.snp.matrix <- rhierbaps::load_fasta(abortus.aln)
```


#Running hierBAPS

```{r}
hb.allBabo.results <- rhierbaps::hierBAPS(all.snp.matrix, max.depth = 4, n.pops = 20, quiet = TRUE)
head(hb.allBabo.results$partition.df)
```


#Plotting results

```{r}
abortus_all.tre <- system.file("BabCR", "abortus_all.tre", package = "rhierbaps")

allab_tree <- phytools::read.newick(abortus_all.tre)

```

#Simple coloured tree

```{r}
gg_all <- ggtree(allab_tree, layout = "rectangular")
gg_all <- gg_all %<+% hb.allBabo.results$partition.df
gg_all <- gg_all + geom_tippoint(aes(color = factor(`level 1`)))
gg_all
```

#Label tree

```{r}
gg_all2 <- ggtree(allab_tree, layout = "rectangular", branch.length = "none")
gg_all2 <- gg_all2 %<+% hb.allBabo.results$partition.df
gg_all2 <- gg_all2 + geom_tippoint(aes(color = factor(`level 1`)))
gg_all2 <- gg_all2 + theme(legend.position = "right")
gg_all2 <- gg_all2 + geom_tiplab(aes(label = `level 2`), size = 1, offset = 1)
gg_all2
```


#Subclusters zoom

```{r}
plot_sub_cluster(hb.allBabo.results, allab_tree, level = 1, sub.cluster = 1)
```


#Subclusters zoom, letter change

```{r}
hb.object <- hb.allBabo.results
tree <- allab_tree
level <- 1
sub.cluster <- 1
```

```{r}
level <- level+1
cluster.isolate <- hb.object$partition.df$Isolate[hb.object$partition.df[,level]==sub.cluster]
```

#Need to create a tempfile to suprres the output of gzoom
```{r}
ff <- tempfile()
grDevices::png(filename = ff)
gg2 <- ggtree::gzoom(tree,focus = which(tree$tip.label %in% cluster.isolate))
grDevices::dev.off()
unlink(ff)
```

```{r}
temp_column_id <- paste(c("factor(`level ", level, "`)"), collapse = "")
```

```{r}
p2 <- gg2$p2
```

#Remove the old tip lables
```{r}
gg2$p2$layers <- gg2$p2$layers[-3]
```

#Add new labels
```{r}
p2 <- p2 + ggtree::geom_tiplab(size=1)
```

```{r}
p2 <- ggtree::`%<+%`(p2, hb.object$partition.df)
p2 <- p2 + ggtree::geom_tippoint(ggplot2::aes_string(color=temp_column_id))
p2 <- p2+ ggplot2::labs(color=temp_column_id) + ggplot2::theme(legend.position="right") 
p2
```


```{r}
ggtree::multiplot(gg2$p1, p2, ncol = 2)
```






